### 2015-10-12 Projects/DelCo_2015/Report/hose_report.tex
Added Hose disclaimer and a few more convertions

\memofrom{NIST Firefighting Technology Group} % Sender(s)

@@

This letter report documents two experiments performed at the request of NFPA staff for use by the NFPA Technical Committee on Fire Hose.   The objective of the experiments was to gain some insight into the failure of fire hose as a result of thermal insult.  Three different hose conditions were examined; hose filled with air, hose filled with water, hose flowing 150~gpm of water.

@@

\section{Hose}
The fire hose that was used for the experiments was ``Big - 10'' brand manufactured by Key Hose. According to the manufacturer the hose meets or exceeds all of the performance requirements of NFPA 1961. The ``1 3/4"~in. hose is constructed with 100 polyester double jacket and the rubber lining is made of a single-ply extruded tube of synthetic EPDM a minimum wall thickness of 0.040~in. The hose condition was new, right out of the box. See Attachment 1 for further hose information.

@@

\section{Results}
Two experiments were conducted to examine the amount of thermal exposure required to cause the fire hose to burn through. In each experiment three different hose conditions were examined: hose filled with air, hose filled with water, hose flowing 150 gpm of water. The difference between the two experiments was the location of the exposed hose section. In Experiment 1 the center of the exposed hose section and instrumentation was located 11 ft from the open doorway on Side C. In Experiment 2 the exposed hose section and instrumentation was located 4~ft from the open doorway on Side C.

>>>>

\memofrom{Daniel Madrzykowski \\ Craig Weinschenk \\ NIST Firefighting Technology Group} % Sender(s)

@@

This letter report documents two experiments performed at the request of NFPA staff for use by the NFPA Technical Committee on Fire Hose.   The objective of the experiments was to gain some insight into the failure of fire hose as a result of thermal insult.  Three different hose conditions were examined; hose filled with air, hose filled with water, hose flowing 568~lpm (150~gpm) of water.

@@

\section{Hose}
The fire hose that was used for the experiments was ``Big - 10'' brand manufactured by Key Hose. According to the manufacturer the hose meets or exceeds all of the performance requirements of NFPA 1961. The ``1 3/4"~in. hose is constructed with 100 polyester double jacket and the rubber lining is made of a single-ply extruded tube of synthetic EPDM a minimum wall thickness of 0.040~in. The hose condition was new, right out of the box. See Attachment 1 for further hose information. Note that the brand name of this material was included for purposes of explaining the experiment. Identification in this report is not intended to imply recommendation or endorsement by NIST, nor is it intended to imply that such materials are necessarily the best available for the purpose.

@@

\section{Results}
Two experiments were conducted to examine the amount of thermal exposure required to cause the fire hose to burn through. In each experiment three different hose conditions were examined: hose filled with air, hose filled with water, hose flowing 150 gpm of water. The difference between the two experiments was the location of the exposed hose section. In Experiment 1 the center of the exposed hose section and instrumentation was located 3.4~m (11.2~ft) from the open doorway on Side C. In Experiment 2 the exposed hose section and instrumentation was located 1.2~m (4~ft) from the open doorway on Side C.
